\sysfull

### 2017-08-11 paper/evaluation.tex
work on evaluation section

The applications that were used in the evaluation are: (i) \textbf{Bitcount}: counts bits in byte pseudo-random string using varying algorithms. Each result is compared for correctness; (ii) \textbf{Cold chain}: emulates an embedded temperature sensing engine: measurements are randomly generated and are compressed using a LZW algorithm for x-entry dictionary and y-byte block; (iii) \textbf{Cuckoo}: implements cuckoo filter---x entry filter filled to y of capacity---the program first stores a sequence of pseudo-random numbers, then queries the filter to recover it; (iv) \textbf{RSA}: encrypts predefined x byte long string with a y bytes long key\todo{were keys of 64 bytes tested? If yes: do they exhaust energy}{Amjad}. This set of benchmarks is the same as used in~\cite{chain,alpaca}\todo{Fill-in the missing data and verify its correctness}{Przemek/Amjad}. In addition to Chain benchmarks new applications were implemented: (v) \textbf{DFT}, (vi) \textbf{Huffman compressor}, and (vii) \textbf{Selection Sort}. All applications are compared in Table~\ref{table:benchmark_list} in terms of source lines of code against Chain.

\begin{table}[t]
	\centering
	\footnotesize
	\begin{tabular}{|c|c|c|}
		\hline
		Nickname (abbreviation) & SLOC (\sys) & SLOC (Chain~\cite{chain})\\
		\hline\hline
		Bitcount (bc) & 351 & 588 \\ %59\%
		Cold chain (cem) & 388 & 721 \\ %53\%
		Cuckoo (cuckoo) & 483 & 762 \\ %63\%
		RSA (rsa) & 887 & 1233 \\ %71\%
		Activity (ar) & 483 & 762 \\ %63\%
		DFT (dft) & {} & {} \\ %Two resolutions: 4 and 8 Bytes
		Huffman (dd) & {} & {} \\ %Data decompression size: 100 bytes
		Selection sort (sort) & {} & {} \\
		\hline
	\end{tabular}
\caption{List of benchmark programs used in \sys evaluation; SLOC: source lines of code.}
\label{table:benchmark_list}
\end{table}

\subsection{Evaluation Results}
\label{sec:results_evaluation}

\subsubsection{Compiler Performance}
\label{sec:results_compiler}

\begin{table}[t]
	\centering
	\footnotesize
	\begin{tabular}{|c|c|c|c|c|c|c|c|}
		\hline
		{} & \multicolumn{2}{l|}{{PVAR size (Byte)}} & \multicolumn{2}{c|}{{No. tasks}} & \multicolumn{2}{c|}{{No. paging code}} \\
		\hline
		Nickname & Hand & Comp. & Hand & Comp. & Hand & Comp. \\
		\hline\hline
		Bitcount & 22 & 22 & 10 & 15 & 81 & 93 \\
		Cold chain & 3492 & 3242 & 12 & 9 & 92 & 123 \\
		Cuckoo & 282 & 288 & 15 & 6 & 90 & 76 \\
		RSA & 332 & 250 & 20 & 27 & 130 & 296 \\
		AR & 166 & 218 & 11 & 6 & 112 & 333 \\
		Sort & 104 & 104 & 4 & 2 & 70 & 23 \\
		\hline
	\end{tabular}
	\caption{Comparison between compiler-generated \sys code (Comp.) and hand-written \sys code (Hand).}
\label{table:compiler_result}
\end{table}

@@

Additionally, we evaluated the compile time for automatic task generation per application\footnote{We could not compile DFT application since the LLVM inserts mathematical built-in functions (i.e. \texttt{\_\_muldf3}, \texttt{\_\_floatsidf}, \texttt{\_\_adddf3}) whose implementation were not provided by the LLVM MSP430 back-end.}. We compiled the apps on a 4-core virtual machine with 1\,GB memory with Arch Linux, running on Intel Core i5-6200U (2.30\,GHz) processor. The result are given in Table~\ref{table:compile_time}. We used a {\em date}\todo{date or time?}{Kiwan} linux command to measure the rough time. Most of the compile time was due to pointer aliasing, when calculating possible live ranges of variables. Apps such as RSA whose code size is large and uses a lot of variables, need longer compilation time due to a larger search space for pointer aliasing.

\begin{table}[t]
	\centering
	\footnotesize
	\begin{tabular}{|c|c|c|c|c|c|}
		\hline
		Bitcount & Cold chain & Cuckoo & RSA & AR & Sort \\
		\hline\hline
		3 & 2 & 6 & 86 & 34 & < 1 \\
		\hline
	\end{tabular}
	\caption{\sys compile time per application (seconds).}
\label{table:compile_time}
\end{table}

@@

\subsubsection{\sys Performance}
\label{sec:result_coalescing}

@@

Experimental evaluation of task coalescing mechanism under intermittent power of \sys is given in Figure~\ref{fig:coalescing}. For each application we measured execution time (with and without task coalescing) at \{20, 40, 60\}\,cm distance between RFID antenna and WISP and when WISP was powered directly from FET. Each measurement was repeated x times per each distance/application. From the result we clearly see an enormous benefit of coalescing, especially at large WISP to RFID reader antenna distance ($\approx$56\% for cem, 100\% for sort and $\approx$400\% for bc). At each distance, \sys coalescing mechanism provided faster execution times compared to non-coalescing case. \todo{Discuss different shapes per app}{Amjad}

>>>>

The applications that were used in the evaluation are: (i) \textbf{bc}: counts bits in byte pseudo-random string using varying algorithms. Each result is compared for correctness; (ii) \textbf{cem}: emulates an embedded temperature sensing engine: measurements are randomly generated and are compressed using a LZW algorithm for  fixed entry dictionary and fixed byte block; (iii) \textbf{cuckoo}: implements Cuckoo filter---the program first stores a sequence of pseudo-random numbers, then queries the filter to recover it; (iv) \textbf{rsa}: encrypts predefined string with a predefined key; (v) \textbf{ar} performs nearest neighbour classification using randomly generated sequence of three-axes accelerometer data. This set of benchmarks is the same as used in~\cite{chain,alpaca}. In addition to Chain benchmarks new applications were implemented: (vi) \textbf{dft}: discreet Fourier transform, (vii) \textbf{dd}: Huffman-based data decompression, and (viii) \textbf{sort}: selection sort algorithm. All applications are compared in Table~\ref{table:benchmark_list} in terms of source lines of code against Chain.

\begin{table}[t]
	\centering
	\footnotesize
	\begin{tabular}{|c|c|c|}
		\hline
		Application & SLOC (\sys) & SLOC (Chain~\cite{chain})\\
		\hline\hline
		{bc} & 351 & 588 \\ %59\%
		{cem} & 388 & 721 \\ %53\%
		{cuckoo} & 483 & 762 \\ %63\%
		{rsa} & 887 & 1233 \\ %71\%
		{ar} & 483 & 762 \\ %63\%
		{dft} & {} & {} \\ %Two resolutions: 4 and 8 Bytes
		{dd} & {} & {} \\ %Data decompression size: 100 bytes
		{sort} & {} & {} \\
		\hline
	\end{tabular}
\caption{List of benchmark programs used in \sys evaluation; SLOC: source lines of code.}
\label{table:benchmark_list}
\end{table}

\subsection{\sys Evaluation Results}
\label{sec:results_evaluation}

\subsubsection{\sys Compiler Performance}
\label{sec:results_compiler}

\begin{table}[t]
	\centering
	\footnotesize
	\begin{tabular}{|c|c|c|c|c|c|c|c|}
		\hline
		{} & \multicolumn{2}{l|}{{PVAR size (Byte)}} & \multicolumn{2}{c|}{{No. tasks}} & \multicolumn{2}{c|}{{No. paging code}} \\
		\hline
		Nickname & Hand & Comp. & Hand & Comp. & Hand & Comp. \\
		\hline\hline
		bc & 22 & 22 & 10 & 15 & 81 & 93 \\
		cem & 3492 & 3242 & 12 & 9 & 92 & 123 \\
		cuckoo & 282 & 288 & 15 & 6 & 90 & 76 \\
		rsa & 332 & 250 & 20 & 27 & 130 & 296 \\
		ar & 166 & 218 & 11 & 6 & 112 & 333 \\
		sort & 104 & 104 & 4 & 2 & 70 & 23 \\
		\hline
	\end{tabular}
	\caption{Comparison between compiler-generated \sys code (Comp.) and hand-written \sys code (Hand).\todo{Data for Huffman in Table 5 and 6 is missing}{Kiwan}}
\label{table:compiler_result}
\end{table}

@@

Additionally, we evaluated the compile time for automatic task generation per application\footnote{We could not compile the DFT application since LLVM inserts mathematical built-in functions (i.e. \texttt{\_\_muldf3}, \texttt{\_\_floatsidf}, \texttt{\_\_adddf3}) whose implementation were not provided by the LLVM MSP430 back-end.}. We compiled the apps on a 4-core virtual machine with 1\,GB memory with Arch Linux, running on Intel Core i5-6200U (2.30\,GHz) processor. The result are given in Table~\ref{table:compile_time}. We used a {\em date}\todo{date or time?}{Kiwan} linux command to measure the rough time. Most of the compile time was due to pointer aliasing, when calculating possible live ranges of variables. Apps such as RSA whose code size is large and uses a lot of variables, need longer compilation time due to a larger search space for pointer aliasing.

\begin{table}[t]
	\centering
	\footnotesize
	\begin{tabular}{|c|c|c|c|c|c|}
		\hline
		bc & cem & cuckoo & rsa & ar & sort \\
		\hline\hline
		3 & 2 & 6 & 86 & 34 & < 1 \\
		\hline
	\end{tabular}
	\caption{\sys compile time per application (seconds).}
\label{table:compile_time}
\end{table}

@@

\subsubsection{\sys Runtime Performance}
\label{sec:result_coalescing}

@@

Experimental evaluation of task coalescing mechanism under intermittent power of \sys is given in Figure~\ref{fig:coalescing}. For each application we measured execution time (with and without task coalescing) at \{20, 40, 60\}\,cm distance between RFID antenna and WISP and when WISP was powered directly from FET. Each measurement was repeated x times per each distance/application. From the result we clearly see an enormous benefit of coalescing, especially at large WISP to RFID reader antenna distance ($\approx$56\% for cem, 100\% for sort and $\approx$400\% for bc). At each distance, \sys coalescing mechanism provided faster execution times compared to the non-coalescing case. \todo{Discuss different shapes per app}{Amjad}
